Why Real-World Subgraph Isomorphism is Easy, \\ and What This Means for Graph Databases

### 2016-10-20 paper/paper.tex
Typo

Our first contribution is to present and evaluate a new method for creating random pattern/target
pairs. This method generates both satisfiable and unsatisfiable instances, and can produce
computationally challenging instances with only a few tens of vertices in the pattern, and 150
vertices in the target. This is not entirely straightforward---the lack of unsatisfiable instances
for testing purposes cannot be addressed simply by using taking a pattern graph from one of the
existing random suites with the ``wrong'' target graph, as this tends to give either a trivially
unsatisfiable instance, or a satisfiable instance. (In particular, it is \emph{not} the case that a
relatively small random graph is unlikely to appear in a larger random graph.)

>>>>

Our first contribution is to present and evaluate a new method for creating random pattern/target
pairs. This method generates both satisfiable and unsatisfiable instances, and can produce
computationally challenging instances with only a few tens of vertices in the pattern, and 150
vertices in the target. This is not entirely straightforward---the lack of unsatisfiable instances
for testing purposes cannot be addressed simply by taking a pattern graph from one of the
existing random suites with the ``wrong'' target graph, as this tends to give either a trivially
unsatisfiable instance, or a satisfiable instance. (In particular, it is \emph{not} the case that a
relatively small random graph is unlikely to appear in a larger random graph.)
